Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
wording

It also appears that the averaging over the low-pass filter designs and the
threshold values increases significantly the quality of the infered network
according to both metrics.

@@

If one would infer perfectly the undirected network, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small AUROC gain. The area under the ROC curve is not a consistent metric
with respect to the problem statement.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
Trying to detect the link direction is more penalizing than rewarding.

For these reasons, we strongly advice to avoid the AUROC
for the assessment network inference using a more appropriate
metric such as the area under the precision-recall curve (AUPRC). Those
conclusions are in line with \cite{schrynemackers2013protocols}.

>>>>

It also appears that the averaging over the low-pass filter designs and the
threshold values increases significantly the quality of the inferred network
according to both metrics.

@@

If the undirected network is perfectly, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small gain.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
Trying to detect the link direction is more penalizing than rewarding.

The area under the ROC curve is not consistent metric
with respect to the problem statement. We strongly advice to avoid the AUROC
for the assessment of network inference method. An alternative metric would
be to use the area under the precision-recall curve (AUPRC). Those
conclusions are in line with \cite{schrynemackers2013protocols}.
